workshop

### 2023-02-15 scripts/workshop/dynamics.Rmd
add figure and update ggplot

```{r}
ggplot()+
  geom_line(data=output_x,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_c, mapping=aes(y=I,x=time, color=color_c))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_a, mapping=aes(y=I,x=time, color=color_a))+
  scale_color_manual(name="",values = "yellow")+
  new_scale_color()+
  geom_line(output_h, mapping=aes(y=I,x=time, color=color_h))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n, mapping=aes(y=I,x=time, color=color_n))+
  scale_color_manual(name="",values = "gray")+
  labs(y="N",x="Time")+
  ylim(0,30)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions"))+
  theme_bw()
```

>>>>

```{r}
ggplot()+
  geom_line(data=output_x,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_c, mapping=aes(y=I,x=time, color=color_c))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_a, mapping=aes(y=I,x=time, color=color_a))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_h, mapping=aes(y=I,x=time, color=color_h))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n, mapping=aes(y=I,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,30)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions"))+
  theme_bw()
```

### 2023-02-15 scripts/workshop/workshop.Rmd
add figure and update ggplot

incidence %>% ggplot(.,aes(x=Month.1, y=incidence)) + geom_col() + facet_grid(vars(WetAltID))
incidence %>% ggplot(.,aes(x=Month.1, y=incidence, group = 1)) + geom_point() + geom_line() + facet_wrap(~WetAltID, nrow = 5, ncol = 4)
```

```{r}
comm_data <- readRDS(here("processed_data","comm_data.rds"))
comm_data %>% ungroup() %>% ggplot(.,aes(x=Month.1, y=Prevalence, group = 1)) + geom_point() + geom_line() + facet_wrap(~WetAltID, nrow = 5, ncol = 4)
```

>>>>

incidence %>% ggplot(.,aes(x=Month.1, y=incidence)) + geom_col() + facet_grid(vars(WetAltID))
incidence %>% ggplot(.,aes(x=Month.1, y=incidence, group = 1)) + geom_point() + geom_line() + facet_wrap(~WetAltID, nrow = 5, ncol = 4) + labs(title="Incidence over time")
```

```{r}
comm_data <- readRDS(here("processed_data","comm_data.rds"))
comm_data %>% ungroup() %>% ggplot(.,aes(x=Month.1, y=Prevalence, group = 1)) + geom_point() + geom_line() + facet_wrap(~WetAltID, nrow = 5, ncol = 4) + labs(title="Prevalence over time")
```

```{r}
comm_data %>% ungroup() %>% ggplot(.,aes(x=Month.1, y=log10(size), group = 1)) + geom_point() + geom_line() + facet_wrap(~WetAltID, nrow = 5, ncol = 4) + labs(title="log10(Abundance) over time")
```
